Late Pleistocene stone artefact technology at Mau A, Yen Bai, Northern Vietnam

### 2022-03-25 analysis/paper/paper.Rmd
Added clarification on how k is chosen with univariate k-means
Update to environmental context

-Further context from (McAdams et al, 2020)

@@

Mass clusters were generated using univariate k-means, with the end result being 6 mass clusters, with mass cluster 1 having the least mass on average and 6 having the greatest mass on average. Univariate k-means is a non-hierarchical clustering technique that creates a set number of groups equal to k, with points being assigned to groups in such a manner that the total distances between each point and mean of the group is minimized. We used the Ckmeans.1d.dp package in R to perform our univariate k-means analysis (Wang & Song, 2011). The Ckmeans.1d.dp has been used for univariate clustering in applications outside of archaeology (Song & Zhong, 2020).

@@

>>>>

While early hominins reached Mainland Southeast Asia as early as 800 ka ago (Forestier et al., 2022), the

Mainland Southeast Asia 
-Further context from (McAdams et al, 2020)

@@

Mass clusters were generated using univariate k-means, with the end result being 6 mass clusters, with mass cluster 1 having the least mass on average and 6 having the greatest mass on average. Univariate k-means is a non-hierarchical clustering technique that creates a set number of groups equal to k, with points being assigned to groups in such a manner that the total distances between each point and mean of the group is minimized. The algorithm used for univariate k-means calculates the optimum number of groups. We used the Ckmeans.1d.dp package in R to perform our univariate k-means analysis (Wang & Song, 2011). The Ckmeans.1d.dp has been used for univariate clustering in applications outside of archaeology (Song & Zhong, 2020).

@@

Forestier, H., Zhou, Y., Sophady, H., Li, Y., Codeluppi, D., Auetrakulvit, P., & Zeitoun, V. (2022). The first lithic industry of mainland Southeast Asia: Evidence of the earliest hominin in a tropical context. L’Anthropologie, 126(1), 102996. https://doi.org/10.1016/j.anthro.2022.102996
